\documentclass[]{resume-openfont}
\usepackage{fancyhdr}
\usepackage{multicol}
\pagestyle{fancy}
\fancyhf{}

\begin{document}

% Personal Information Section
\begin{minipage}[t]{1\textwidth} 
\namesection{}{Nicholas Wanner}{
    \href{mailto:nickrwann@gmail.com}{nickrwann@gmail.com} | 832.349.0727 | www.linkedin.com/in/nick-wanner
}
\end{minipage}

\vspace{2 mm}

\begin{minipage}[t]{0.4\textwidth} 
    % Education - This will take up one-third of the width
    \section{\Large Education} 
    \subsection{Texas A\&M University}
    \descript{BS in Computer Engineering}
    \descript{\normalsize Minor in Cyber Security}
    \location{May 2021 | College Station, TX}
    \location{GPA: 3.94 / 4.0 (Summa Cum Laude)}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.6\textwidth}
    % Skills - This section will now take up 60% of the text width
    \section{\Large Skills}
        \begin{tabular}{@{}l l}
            \textbf{Languages}: & C/C++, Python, C\#, JavaScript, CSS \\
            \textbf{Databases}: & SQL, NoSQL (e.g., PostgreSQL, MongoDB) \\
            \textbf{Web Dev}: & ASP.NET, Vue.js, Express \\
            \textbf{DevOps}: & Git, Docker, Kubernetes, Azure \\
            \textbf{Machine Learning \& AI}: & Tensorflow, Huggingface, ONNX Runtime \\
            \textbf{Other}: & WSL, Databricks \\
        \end{tabular}
\end{minipage}


% Experience Section
\begin{minipage}[t]{1\textwidth}
\section{Experience}
\titlerule
\vspace{2.5 mm}

% Dell Experience 1
\runsubsection{Dell}
\descript{| Software Engineer, CTO Software PoC Team }
\location{June 2022 - Present | Austin, TX}
\vspace{\topsep}
\begin{tightemize}
    \item Spearheaded an AI/ML model optimization initiative using ONNX Runtime and advanced quantization tools, achieving significant compute performance boost for targeted hardware as well as halving model storage requirements for client-formfactor laptops.
    \item Designed and implemented versatile MLOps templates and platforms in Databricks, tailored for developers and data scientists in data-centric roles, additionally integrating advanced data/model drift detection to enhance performance and operational efficiency.
    \item Secured five patents in wireless and HID tech, including WiFi meshes and gaming router enhancements.
    \item Enhanced gaming experiences by minimizing latency jitter with advanced networking solutions for critical applications.
    \item Developed embedded code for 'NYX' wireless PC controller, improving user experience and connectivity at CES 2022.
    \item Developed a PoC for better workstation setups, creating an algorithm for optimal peripheral configurations.    
\end{tightemize}
\sectionsep

% Dell Experience 2
\runsubsection{Dell}
\descript{| Software Engineer, CTO Tech Strategy Team }
\location{June 2021 - June 2022 | Austin, TX}
\begin{tightemize}
    \item Led a proof-of-concept for a Dell Bluetooth pairing solution, enhancing connectivity and redefining pairing experiences.
    \item Aided in creating ML-driven thermal management, improving compute efficiency by 12\% and extending battery life by 15\%.
    \item Engineered a data collection framework to streamline gathering of training data and assess system setting impacts.
    \item Collaborated with data scientists on defining workloads and metrics, crucial to models adapting performance to user needs.
\end{tightemize}
\sectionsep

% Dell Internship
\runsubsection{Dell}
\descript{| Software Engineer Intern }
\location{June 2020 - Aug 2020 | Austin, TX}
\begin{tightemize}
    \item Led touchpad prototype design, significantly boosting user interaction, efficiency, and halving time to market.
    \item Pioneered touchpad technology leading to a patent, highlighting its innovation and intellectual value.
    \item Conducted research on pen-on-touchpad technology, evaluating pen types and establishing KPIs.
\end{tightemize}
\sectionsep

% Thought Trace Internship
\runsubsection{Thought Trace}
\descript{| Data Science Intern}
\location{Jan 2018 – Aug 2018 | Houston, TX}
\begin{tightemize}
    \item Developed web apps for machine learning data labeling and QA, improving data accuracy and process efficiency.
    \item Created a comprehensive ontology for front-end UI validation, improving application reliability and user experience.
    \item Engaged in SCRUM meetings and collaborated with data scientists, fostering team dynamics and project success.
\end{tightemize}
\sectionsep

% Texas A&M Teaching
\runsubsection{Texas A\&M}
\descript{| Peer Teacher }
\location{June 2019 – Aug 2019 | College Station, TX}
\begin{tightemize}
    \item Instructed 35 students in {\it Intro to Computer Systems}
    \item Developed adaptive lesson plans to engage a variety of learning styles, enhancing both personal and group involvement.    
\end{tightemize}
\sectionsep

\end{minipage}


% Projects Section
\begin{minipage}[t]{1\textwidth}
\vspace{-4 mm}
\section{Projects}
\titlerule
\vspace{2.5 mm}

% Project 1
\runsubsection{Multi-Instrumental Tactile Synthesizer (MITS)}
\descript{| Tools: Arduino, Swift, Reaper (DAW)}
Gloves that convert hand gestures into musical instrument sounds, utilizing Arduino and DAW software, demonstrating gesture recognition and sound synthesis.
\sectionsep

% Project 2
\runsubsection{Receipt Reader}
\descript{| Tools: Node JS, HTML, CSS, Google APIs}
Web app enabling users to authenticate, upload receipts, and extract data with OCR, with seamless Google Sheets integration for expense tracking and analysis.
\sectionsep

\end{minipage} 

\end{document}
