\documentclass[10pt]{resume-openfont}
% \usepackage[margin=0.75in]{geometry}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{setspace}
\setstretch{0.9}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % Removes the horizontal line in the header
\setlength\headheight{14pt}
\setlength\footskip{14pt}

\begin{document}

% Personal Information Section
\begin{minipage}[t]{1\textwidth} 
\namesection{}{Nicholas Wanner}{
    \href{mailto:nickrwann@gmail.com}{nickrwann@gmail.com} | 832.349.0727 | www.linkedin.com/in/nick-wanner
}
\end{minipage}

\vspace{1mm} % Reduced space

% Three-column Layout: Education, Skills
\begin{minipage}[t]{1\textwidth} 
\begin{multicols}{2}
    % Education
    \section{\Large Education} 
    \subsection{Texas A\&M University}
    \descript{BS in Computer Engineering}
    \descript{\normalsize Minor in Cyber Security}
    \location{May 2021 | College Station, TX}
    Summa Cum Laude \\
    \location{GPA: 3.94 / 4.0}
    \sectionsep
    
    \columnbreak
    
    % Skills
    \section{\Large Skills}
    \subsection{Languages}
    Python \textbullet{} C/C++ \textbullet{} C\# \\
    JavaScript \textbullet{} CSS
    \subsection{Tools}
    Azure \textbullet{} Databricks \textbullet{} Git/Github/Bitbucket/Gitlab \\ 
    ONNX \textbullet{} Numpy \textbullet{} Pandas \\
    GraphQL \textbullet{} MongoDB
    PyTorch \textbullet{} Tensorflow
    \sectionsep

\end{multicols}
\end{minipage} 

\vspace{-3mm} % Reduced space

% Experience Section
\begin{minipage}[t]{1\textwidth}
\section{Experience}
\titlerule
\vspace{1mm} % Reduced space

% Dell Experience 1
\runsubsection{Dell}
\descript{| Software Engineer, CTO Software PoC Team }
\location{June 2022 - Present | Austin, TX}
\begin{tightemize}
\item Spearheaded an AI/ML model optimization initiative using ONNX Runtime and advanced quantization tools, achieving a Y\% improvement in model performance and efficiency for targeted hardware applications.
\item Assisted in building an MLOps pipeline in Databricks, migrating model data and introducing data/model drift detection to monitor performance.
\item Secured five patents in wireless tech and HID innovations, including WiFi meshes, gaming router optimizations, and touchpad controls.
\item Investigated and implemented advanced networking solutions to minimize gaming latency jitter, elevating user experience for performance-critical applications.
\item Supported developing embedded code for the 'NYX' wireless PC controller, showcased at CES 2022, enhancing user experience and connectivity.
\item Contributed to a PoC project aimed at refining workstation setups, crafting an algorithm that recommends peripheral configurations based on user preferences and system capabilities.
\end{tightemize}
\sectionsep

% Dell Experience 2
\runsubsection{Dell}
\descript{| Software Engineer, CTO Tech Strategy Team }
\location{June 2021 - June 2022 | Austin, TX}
\begin{tightemize}
\item Spearheaded the investigation and proof-of-concept for a proprietary Bluetooth pairing solution for Dell devices, streamlining connectivity and setting a new standard in device pairing experiences.
\item Contributed to developing ML-driven dynamic thermal management systems, achieving a 12\% boost in efficiency and 15\% longer battery life by adapting system thermals to workload demands.
\item Engineered a data collection framework to streamline gathering of training data and assess system setting impacts.
\item Collaborated with data scientists to define workloads and key data metrics, playing a pivotal role in models that adapt system performance to real-time user needs.
\item Collaborated with vendors and stakeholders in the design and integration of advanced camera technologies for new product incubations, enhancing client system capabilities.
\end{tightemize}
\sectionsep

% Dell Internship
\runsubsection{Dell}
\descript{| Software Engineer Intern }
\location{June 2020 - Aug 2020 | Austin, TX}
\begin{tightemize}
\item Led the design of a novel touchpad technology prototype using C\# and .NET, significantly enhancing user interaction and efficiency, and accelerated the project timeline from over two years to just one, expediting time to market.
\item Pioneered the touchpad technology that led to a successful patent filing, underlining its innovation and value as intellectual property.
\item Conducted research and user studies for pen-on-touchpad technology, evaluating multiple pen technologies and establishing KPIs for project success.
\end{tightemize}
\sectionsep

% Texas A&M Teaching
\runsubsection{Texas A\&M}
\descript{| Peer Teacher }
\location{June 2019 – Aug 2019 | College Station, TX}
\begin{tightemize}
\item Taught {\it Intro to Computer Systems} to a class of 35 students, effectively communicating core concepts and fostering a collaborative learning environment.
\item Designed and tailored lesson plans to accommodate diverse learning styles, promoting both individual and group engagement.
\end{tightemize}
\sectionsep

% Thought Trace Internship
\runsubsection{Thought Trace}
\descript{| Data Science Intern}
\location{Jan 2018 – Aug 2018 | Houston, TX}
\begin{tightemize}
\item Developed web applications to streamline machine learning data labeling and QA processes, enhancing data accuracy and efficiency.
\item Created a comprehensive ontology for front-end UI validation, improving application reliability and user experience.
\item Actively participated in SCRUM meetings and collaborated with data scientists on problem-solving, contributing to a cohesive team dynamic and project success.
\end{tightemize}
\sectionsep

\end{minipage}

% Projects Section
\begin{minipage}[t]{1\textwidth}
\vspace{-4 mm}
\section{Projects}
\titlerule
\vspace{2.5 mm}

% Project 1
\runsubsection{Multi-Instrumental Tactile Synthesizer (MITS)}
\descript{| Tools: Arduino, Swift, Reaper (DAW)}
Developed "Multi-Instrumental Tactile Synthesizer" (MITS) gloves that convert hand gestures into musical instrument sounds, utilizing Arduino and DAW software, demonstrating innovative application of gesture recognition and sound synthesis.
\sectionsep

% Project 2
\runsubsection{Receipt Reader}
\descript{| Tools: Node JS, HTML, CSS, Google APIs}
Engineered a web application for receipt management that allows users to authenticate via Google Identity, upload receipt images, and utilize Google's Vision OCR for text extraction. Implemented a parsing service to delineate items and costs, facilitating user validation before aggregating data into a Google Sheets spreadsheet for long-term tracking and analysis.
\sectionsep

\end{minipage} 
\end{document}
